COG-ED Manuscript

### 2022-01-12 06_Paper/COG-ED/Manuscript.Rmd
tried constructing ggplot for SSA (not done yet)

>>>>

  # add column to data frame, which indexes the Mean+/-SD groups
  h2b_data$nfc_group <- ifelse(h2b_data$nfc.cgm > (mean(h2b_data$nfc.cgm) + sd(h2b_data$nfc.cgm)), "+1 SD",
                               ifelse(h2b_data$nfc.cgm < (mean(h2b_data$nfc.cgm) - sd(h2b_data$nfc.cgm)), "-1 SD", "Mean"))
  # add columns to data frame, which index the max/min value of SV per group
  h2b_data$sv_groupmax <- ifelse(h2b_data$nfc_group == "+1 SD" & h2b_data$level == 2,
                                 max(h2b_data$sv[h2b_data$nfc_group == "+1 SD" & h2b_data$level == 2]),
                                 ifelse(h2b_data$nfc_group == "+1 SD" & h2b_data$level == 3,
                                        max(h2b_data$sv[h2b_data$nfc_group == "+1 SD" & h2b_data$level == 3]),
                                        ifelse(h2b_data$nfc_group == "+1 SD" & h2b_data$level == 4,
                                               max(h2b_data$sv[h2b_data$nfc_group == "+1 SD" & h2b_data$level == 4]),
                                               ifelse(h2b_data$nfc_group == "-1 SD" & h2b_data$level == 2,
                                                      max(h2b_data$sv[h2b_data$nfc_group == "-1 SD" & h2b_data$level == 2]),
                                                      ifelse(h2b_data$nfc_group == "-1 SD" & h2b_data$level == 3,
                                                             max(h2b_data$sv[h2b_data$nfc_group == "-1 SD" & h2b_data$level == 3]),
                                                             ifelse(h2b_data$nfc_group == "-1 SD" & h2b_data$level == 4,
                                                                    max(h2b_data$sv[h2b_data$nfc_group == "-1 SD" & h2b_data$level == 4]),
                                                                    ifelse(h2b_data$nfc_group == "Mean" & h2b_data$level == 2,
                                                                           max(h2b_data$sv[h2b_data$nfc_group == "Mean" & h2b_data$level == 2]),
                                                                           ifelse(h2b_data$nfc_group == "Mean" & h2b_data$level == 3,
                                                                                  max(h2b_data$sv[h2b_data$nfc_group == "Mean" & h2b_data$level == 3]),
                                                                                  max(h2b_data$sv[h2b_data$nfc_group == "Mean" & h2b_data$level == 4])))))))))
  h2b_data$sv_groupmax <- ifelse(h2b_data$nfc_group == "+1 SD" & h2b_data$level == 2,
                                 min(h2b_data$sv[h2b_data$nfc_group == "+1 SD" & h2b_data$level == 2]),
                                 ifelse(h2b_data$nfc_group == "+1 SD" & h2b_data$level == 3,
                                        min(h2b_data$sv[h2b_data$nfc_group == "+1 SD" & h2b_data$level == 3]),
                                        ifelse(h2b_data$nfc_group == "+1 SD" & h2b_data$level == 4,
                                               min(h2b_data$sv[h2b_data$nfc_group == "+1 SD" & h2b_data$level == 4]),
                                               ifelse(h2b_data$nfc_group == "-1 SD" & h2b_data$level == 2,
                                                      min(h2b_data$sv[h2b_data$nfc_group == "-1 SD" & h2b_data$level == 2]),
                                                      ifelse(h2b_data$nfc_group == "-1 SD" & h2b_data$level == 3,
                                                             min(h2b_data$sv[h2b_data$nfc_group == "-1 SD" & h2b_data$level == 3]),
                                                             ifelse(h2b_data$nfc_group == "-1 SD" & h2b_data$level == 4,
                                                                    min(h2b_data$sv[h2b_data$nfc_group == "-1 SD" & h2b_data$level == 4]),
                                                                    ifelse(h2b_data$nfc_group == "Mean" & h2b_data$level == 2,
                                                                           min(h2b_data$sv[h2b_data$nfc_group == "Mean" & h2b_data$level == 2]),
                                                                           ifelse(h2b_data$nfc_group == "Mean" & h2b_data$level == 3,
                                                                                  min(h2b_data$sv[h2b_data$nfc_group == "Mean" & h2b_data$level == 3]),
                                                                                  min(h2b_data$sv[h2b_data$nfc_group == "Mean" & h2b_data$level == 4])))))))))

  h2c_ss.plot <- ggplot(h2b_data, aes(x = level.cwc, y = sv, color = nfc_group, group = nfc_group)) +
    geom_point() +
    geom_smooth(method = interactions::sim_slopes(m1_h2b, pred = level.cwc, modx = nfc.cgm,
                                                  centered = "none", cond.int = T, control.fdr = T, confint = T),
                data = NULL, mapping = aes(fill = nfc_group, alpha = .15), se = TRUE) # the alpha stands for the opacity of the CIs

  h2c_ss.plot <- ggplot(h2b_data, aes(x = level.cwc, y = sv, color = nfc_group, group = nfc_group)) +
    geom_point() +
    geom_ribbon(aes(ymax = sv_groupmax, ymin = sv_groupmin, fill = "band", color = nfc_group), alpha = .15)
